### 2017-11-14 paper/sections/1_introduction.tex
paper: change first figure
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[t]
  \noindent\includegraphics[width=0.5\textwidth]{figures/motivation-regimes.png}\\
  \caption{The keyspace activity for ParSplice using two different growth
rates.  The line shows the rate that EOM minima values are retrieved from the
key-value store (\(y1\) axis) and the points along the bottom show the number
of keys accessed in a 1 second sliding window (\(y2\) axis).
\label{fig:motivation-regimes}}
\end{figure}

In this paper, we design cache management policies for the ParSplice worker,
driven by a detailed analysis of the key-value accesses over the course of a
long running simulation across a variety of initial conditions.
Figure~\ref{fig:motivation-regimes} shows how ParSplice tasks read key-value
pairs from the worker's cache for two different initial conditions of
\(\Delta\), which is the rate that new atoms enter the simulation.  The line is
the read request rate (\(y1\) axis) and the dots along the bottom are the
number of unique keys accessed (\(y2\) axis).  This figure demonstrates that
small changes to \(\Delta\) can have a strong effect on the timing and
frequency with which new EOM minima are discovered and referenced.  The
ParSplice caches on each node are trimmed when memory pressure reaches a
threshold but the number of unique keys accessed in
Figure~\ref{fig:motivation-regimes} suggests that a small cache of EOM minima
should be sufficient.

% What is Mantle
We use the data management language and policy engine from the Mantle
paper~\cite{sevilla:sc15-mantle} to dynamically explore the effects of
different cache management strategies for the changing key-value workloads
generated by ParSplice.  Mantle was originally touted as a programmable file
system metadata load balancer, but we realize now that the collection of
abstractions designed for file systems was a control plane that improved
metadata access. So in this paper we refer to Mantle as a policy engine that
injects policies written in our data management language directly into a
running service and show how this approach is useful for reasoning about and
designing different cache management strategies in ParSplice.  By service, we
mean a system that manages data and responds requests, such as a file system or
key-value store.  Developers write policies for ``when" they want data moved
and ``how much" of the data to move, then the framework executes these policies
whenever a decision needs to be made.  These abstraction help developers
unfamiliar with the domain quickly reason about, develop, and deploy new
policies that control temporal and spatial locality. We show that Mantle:

>>>>

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/cache-management.png}\\

\caption{Using our data management language and Mantle policy engine, we
designed a dynamically sized caching policy for the ParSplice application. The
solution uses knowledge about the application to detect key access patterns and
adjust the cache accordingly. 
\label{fig:cache-management}}
\end{figure}

In this paper, we design cache management policies for the ParSplice worker,
driven by a detailed analysis of the key-value accesses over the course of a
long running simulation across a variety of initial conditions. Our final
solution, shown by the ``Dynamically Sized Cache" line in
Figure~\ref{fig:cache-management}, detects keyspace access patterns and
re-sizes the cache accordingly. Without tuning or parameter sweeps, our
solution saves more memory than a hand-tuned cache without sacrificing
performance.  More importantly, it works for a variety initial conditions
without changing the policy itself.

% What is Mantle
To design more flexible cache management policies, like our ``Dynamically
Sized Cache" policy, we use the data management language and policy engine
from the Mantle paper~\cite{sevilla:sc15-mantle}. This framework allows us to
dynamically explore the effects of different software-defined cache management
strategies for the changing key-value workloads generated by ParSplice.  Mantle
was originally touted as a programmable file system metadata load balancer, but
we realize now that the collection of abstractions designed for file systems
was a control plane that improved metadata access. So in this paper we refer to
Mantle as a policy engine that injects policies written in our data management
language directly into a running service and show how this approach is useful
for reasoning about and designing different cache management strategies in
ParSplice.  By service, we mean a system that manages data and responds
requests, such as a file system or key-value store.  Developers write policies
for ``when" they want data moved and ``how much" of the data to move, then the
framework executes these policies whenever a decision needs to be made.  These
abstractions help developers unfamiliar with the domain quickly reason about,
develop, and deploy new policies that control temporal and spatial locality. We
show that Mantle:

### 2017-11-14 paper/sections/2_parsplice-keyspace-analysis.tex
paper: change first figure
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\subsubsection*{An active but small keyspace} The bars in
Figure~\ref{fig:methodology-keyspace} show \(50-100\times\) as many reads
(\texttt{get()}) as writes (\texttt{put()}).  Worker tasks read the same key
for extended periods because the trajectory can remain stuck in so-called
superbasins composed of tightly connected sets of states. In this case, many
trajectory segments with the same coordinates are needed before the trajectory
moves on.  Writes only occur for the final state of segments generated by
worker tasks; their magnitude is smaller than reads because the caches ignore
redundant write requests. The number of read and write requests are highest at
the beginning of the run when worker tasks generate segments for the same
state, which is computationally cheap (this motivates
Section~\S\ref{sec:dom-specific}).

>>>>

\begin{figure}[t]
  \noindent\includegraphics[width=0.5\textwidth]{figures/motivation-regimes.png}\\
  \caption{The keyspace activity for ParSplice using two different growth
rates.  The line shows the rate that EOM minima values are retrieved from the
key-value store (\(y1\) axis) and the points along the bottom show the number
of keys accessed in a 1 second sliding window (\(y2\) axis).
\label{fig:motivation-regimes}}
\end{figure}

\subsubsection*{An active but small keyspace}
Figure~\ref{fig:motivation-regimes} shows how ParSplice tasks read key-value
pairs from the worker's cache for two different initial conditions of
\(\Delta\), which is the rate that new atoms enter the simulation.  The line is
the read request rate (\(y1\) axis) and the dots along the bottom are the
number of unique keys accessed (\(y2\) axis).  This figure demonstrates that
small changes to \(\Delta\) can have a strong effect on the timing and
frequency with which new EOM minima are discovered and referenced.  The
ParSplice caches on each node are trimmed when memory pressure reaches a
threshold but the number of unique keys accessed in
Figure~\ref{fig:motivation-regimes} suggests that a small cache of EOM minima
should be sufficient.

The bars in
Figure~\ref{fig:methodology-keyspace} show \(50-100\times\) as many reads
(\texttt{get()}) as writes (\texttt{put()}).  Worker tasks read the same key
for extended periods because the trajectory can remain stuck in so-called
superbasins composed of tightly connected sets of states. In this case, many
trajectory segments with the same coordinates are needed before the trajectory
moves on.  Writes only occur for the final state of segments generated by
worker tasks; their magnitude is smaller than reads because the caches ignore
redundant write requests. The number of read and write requests are highest at
the beginning of the run when worker tasks generate segments for the same
state, which is computationally cheap (this motivates
Section~\S\ref{sec:dom-specific}).
